Man's not hot, Man can never be hot

### 2018-01-16 article/ms.tex
fixed serious issue with title /cc @bjnorfolk
suggested edits to agb and s-process paragraph

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{Mans not hot, Man can never be hot}

@@

% What's a barium star (as observed)? What is the s-process

% What causes a barium star? (extrinsic/intrinsic?)

@@

@@

Barium stars as first recognized by \citet{Bidelman1951}, are chemically unique red giants that exhibit envelopes with an overabundance of both carbon, and heavy elements (Z > 30) in comparison to the Sun. The red giants studied here display especially strong s-process enhancement for Ba\Rmnum{2} and Sr\Rmnum{2} at lines 4554\AA \hspace{0.2mm} and 4077\AA, respectively. (thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?). The slow neutron capture process (s-process), occuring in the interior of AGB (asymptotic giant branch) stars, synthesizes roughly half of all elements heavier than iron \citep[e.g.][]{busso1999,travaglio2001,
herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
karakas12016}. Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions. The energy from the thermal pulses force the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermal pulse driven convective zones. This expansion and resultsing inward movement is classified as the third dredge up (TDU), and is theorized to occur after each thermal pulse. During the TP-AGB phase, enrichent on the surface in $^{12}$C and heavy elements produced by the s-process is a result of the repeated downwash extensions of TDU \citep[e.g.][]{busso2001}. Post TDU, the star contracts and reignites the H-shell producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the intitial mass, composition and mass-loss rate of the star.

@@

>>>>

\usepackage{color}
\newcommand{\todo}[1]{\textcolor{red}{#1}}

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{Man's not hot, Man can never be hot}

@@

% What's a barium star (as observed)?% What causes a barium star? (extrinsic/intrinsic?)

Barium stars are chemically unusual red giants with an overabundance of carbon and heavy elements ($Z > 30$) relative to the Sun \citep{Bidelman1951}. \todo{Explain why this chemical signature is unusual: because this signature can really only be produced by TP-AGB stars, but we see barium stars that have not evolved to the AGB stars. Introduce extrinsic/intrinsic. Barium stars are considered to have been polluted by a binary TP-AGB star, or they are TP-AGB stars themselves.}

@@

About half of all heavy elements are produced by the slow neutron-capture process ($s$-process) inside asymptotic giant branch (AGB) stars \citep[e.g.][]{busso1999,travaglio2001,
herwig2005,romano2010,kobayashi2011,prantzos2012,bisterzo2014,
karakas12016}. 
\todo{This is very good, but the sentence needs splitting up: Late in the AGB phase, during the thermally pulsing-AGB (TP-AGB) phase, thermal instabilities occur in the He shell every $10^5$ years or so, depending on the H-exhausted core mass, and will drive a convective zone that sweeps the entire region lying between the core mass and He-shell; mixing the products of nucleosynthesis within these regions.} The energy from each thermal pulse forces the star to expand, pushing the H-shell out to cooler regions and allowing the convective envelope to move inwards to regions previously mixed by the thermally-driven convective zone. This expansion and resulting inward movement is described as the third dredge up (TDU), and is theorised to occur after every thermal pulse. 
The repeated downwash extensions of TDU cause enhancement of surface $^{12}$C abundance and of other heavy elements produced by the s-process \citep[e.g.,][]{busso2001}. The star contracts after \todo{PDU} and reignites the H-shell, producing the majority of the surface luminosity for the next interpulse period. The interpulse, thermal pulse, and dredge up cycle may occur numerous times and is dependent on the initial mass, composition, and mass-loss rate of the star.

@@

@@

\todo{The red giants studied here display especially strong s-process enhancement for \ion{Ba}{II} and \ion{Sr}{II} at lines 4554\AA\ and 4077\AA, respectively. (thinking I should extend this sentence with a little on the Carbon, maybe I should search for carbon in my figures ?). }
